paper_figures.Rmd

### 2018-01-19 Source/Figures/paper_figures.Rmd
Update paper figures and supplementary materials

# install.packages( 'ggpubr')
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(svglite)
library(ggpubr)
```

@@

@@

## Analyze how filtering the negative genetic interaction by the stringency in fitness score affects the six types of triplet motifs. 
```{r}

@@

print_box_plot_observed_vs_random(negative_interactions_observed, negative_interactions_random, negative_interactions_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

print_box_plot_observed_vs_random(orthomcl_paralogs_observed, orthomcl_paralogs_random, orthomcl_paralogs_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

ggplot_analyze_gi_edges <- ggplot(analyze_gi_edges_counts_gathered, aes(edge_type, counts)) +
	geom_boxplot() +
	## Add the observed values as additional points
	geom_point( data=joined_table_summarized_filtered, aes(x=edge_type, y=observed_counts, color=color ),
				 size=4 , alpha=0.5) 	+
	scale_color_identity()

### With wrapping
ggplot_analyze_gi_edges + 
	## Add faceting
	facet_wrap ( ~ motif_type , scales="free") +
	xlab( "Types of Motifs") 	+ 
	ylab( "Counts") + 
	theme( axis.text.x=element_text(face="italic") ,  strip.text.x=element_text(face="italic"), 
		   text = element_text(size=20)
		   )

ggsave(file.path(figures_results_directory, paste( "analyze_gi_edges_wrap", figure_file_suffix, sep="")), 
	   plot=last_plot(), width=10.3, height=7.5 ) # , width=10, height=7
```

@@

print_box_plot_observed_vs_random(essential_ab_observed, essential_ab_random, essential_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

print_box_plot_observed_vs_random(essential_c_observed, essential_c_random, essential_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

print_box_plot_observed_vs_random(periodic_ab_observed, periodic_ab_random, periodic_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

print_box_plot_observed_vs_random(periodic_c_observed, periodic_c_random, periodic_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

print_box_plot_observed_vs_random(overexpression_ab_observed, overexpression_ab_random, overexpression_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

print_box_plot_observed_vs_random(overexpression_c_observed, overexpression_c_random, overexpression_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour )

@@

motif_type_significance_box_plot_vertical_stack_faceting( result_list$observed_data, 
														  result_list$random_data, 
														  result_list$is_significant, 
														  output_file_name, graphic_width, graphic_height*2)

@@

print_box_plot_observed_vs_random(negative_interactions_observed, negative_interactions_random, negative_interactions_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

@@

>>>>

# install.packages( 'ggpubr')
library(tidyverse)
library(svglite)
library(ggpubr)
```

@@

# Whether to use log y-axis
is_use_log_y_axis <- TRUE

@@

@@

# head( as.data.frame(negative_interactions_observed) + 1)
# temp_random <- negative_interactions_random
# negative_interactions_random[ is.na(negative_interactions_random)] <- 0
# head( as.data.frame(temp_random) + 1)

print_box_plot_observed_vs_random(negative_interactions_observed, negative_interactions_random, negative_interactions_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)

@@

print_box_plot_observed_vs_random(orthomcl_paralogs_observed, orthomcl_paralogs_random, orthomcl_paralogs_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)

@@

analyze_gi_edges_counts_gathered <- dplyr::mutate( analyze_gi_edges_counts_gathered, counts = ifelse( is.na(counts), 1, counts+1) )

joined_table_summarized_filtered <- dplyr::mutate( joined_table_summarized_filtered, observed_counts = observed_counts +1)

ggplot_analyze_gi_edges <- ggplot(analyze_gi_edges_counts_gathered, aes(edge_type, counts))

if (is_use_log_y_axis == TRUE ) {

	ggplot_analyze_gi_edges <- ggplot_analyze_gi_edges + scale_y_log10()
}

ggplot_analyze_gi_edges <- ggplot_analyze_gi_edges +
	geom_boxplot( width = 6) +  # The width parameter changes the width of the boxplot and how the boxplot bunch up together.
	## Add the observed values as additional points
	geom_point( data=joined_table_summarized_filtered, aes(x=edge_type, y=observed_counts, color=color ),
				 size=4 , alpha=0.5) 	+
	scale_color_identity()

### With wrapping
ggplot_analyze_gi_edges <- ggplot_analyze_gi_edges + 
	## Add faceting
	facet_wrap ( ~ motif_type, scales="free") +
	xlab( "Types of Motifs") 	+ 
	ylab( "Counts") + 
	theme( axis.text.x=element_text(face="italic") ,  strip.text.x=element_text(face="italic"), 
		   text = element_text(size=20)
		   )  +  
    scale_x_discrete( )

ggsave(file.path(figures_results_directory, paste( "analyze_gi_edges_wrap", figure_file_suffix, sep="")), 
	   plot=ggplot_analyze_gi_edges, width=10.3, height=7.5 ) # , width=10, height=7
```

@@

print_box_plot_observed_vs_random(essential_ab_observed, essential_ab_random, essential_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)

@@

print_box_plot_observed_vs_random(essential_c_observed, essential_c_random, essential_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)

@@

print_box_plot_observed_vs_random(periodic_ab_observed, periodic_ab_random, periodic_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)

@@

print_box_plot_observed_vs_random(periodic_c_observed, periodic_c_random, periodic_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)

@@

print_box_plot_observed_vs_random(overexpression_ab_observed, overexpression_ab_random, overexpression_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)

@@

print_box_plot_observed_vs_random(overexpression_c_observed, overexpression_c_random, overexpression_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  log_y_axis=is_use_log_y_axis )

@@

motif_type_significance_box_plot_vertical_stack_faceting( result_list$observed_data, 
														  result_list$random_data, 
														  result_list$is_significant, 
														  output_file_name, graphic_width, graphic_height*2, log_y_axis = is_use_log_y_axis )

@@

print_box_plot_observed_vs_random(negative_interactions_observed, negative_interactions_random, negative_interactions_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour, log_y_axis = is_use_log_y_axis )

@@

## Supplementary Figure 3a. 
```{r}

# randomization_collated_counts %>% dplyr::select(one_of(c("motif_type"))) %>% distinct()
# randomization_collated_counts %>% dplyr::filter ( motif_type == "KDKD"  & parameter == 0.2)

motif_types_sorted_by_counts_desc <- c( "PP", "TUTU", "TDP", "PKU",  "KUKU",  "PKD",  
										"PTU", "KDKU", "TDTD", "KDKD", "TDTU", "TUKD", "TDKD", "TDKU", "TUKU" )

summary_for_heatmap <-  randomization_collated_counts %>%
	dplyr::filter (  is.na(motif_type) == FALSE ) %>%
	tidyr::spread( experiment, counts ) %>%
	dplyr::select( one_of( c( "motif_type", "parameter", "Before", "After"))) %>%
	dplyr::mutate( Before=ifelse(is.na(Before),0, Before), 
				   After=ifelse(is.na(After),0, After) ) %>%
	dplyr::group_by( motif_type, parameter ) %>%
	dplyr::summarise ( median_before=median(Before), median_after=median(After) ) %>%
	dplyr::mutate( fold_enrichment_ratio = (median_before + 1)/ (median_after  + 1)) %>%
	dplyr::ungroup()

summary_for_heatmap <- summary_for_heatmap %>%
								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ),
								 				parameter = factor ( parameter, levels = sort ( unique (parameter ))				     ))

stat_test_result_random_edges <- stat_test_result_random_edges %>%
								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ), 
								 			   parameter = factor ( parameter, levels = sort ( unique (parameter )))	, 
								 			   is_significant_star = ifelse( is_significant==1, "*", "")  )

ggplot(summary_for_heatmap, aes(y= motif_type, x= parameter )) +
	geom_raster(aes(fill=(fold_enrichment_ratio) ) ) +
	geom_text(data=stat_test_result_random_edges, aes(label=is_significant_star   )) + 
	scale_fill_gradientn( colors=rev(heat.colors(5))) + #heat.colors
	theme( axis.text.y = element_text(face = "italic")) + 
	guides(fill=guide_colourbar(title="Fold enrichment ratio")) + 
	xlab( "Proportion of negative genetic interactions added or removed") +
	ylab ('Triplet Motif Types')

ggsave(file.path(figures_results_directory, paste("randomization_collated_results_color_by_fold_enrichment", figure_file_suffix, sep="")), plot=last_plot())

# summary_for_heatmap %>% dplyr::filter ( motif_type == "KDKD"  & parameter == 0.2) 
#summary_for_heatmap %>% dplyr::filter ( motif_type == "TUKU"  )

## Supplementary Figure 3b. 
```{r}

motif_types_sorted_by_counts_desc <- c( "PP", "TUTU", "TDP", "PKU",  "KUKU",  "PKD",  
										"PTU", "KDKU", "TDTD", "KDKD", "TDTU", "TUKD", "TDKD", "TDKU", "TUKU" )

stat_test_result_random_edges <- stat_test_result_random_edges %>%
								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ), 
								 			   is_significant_star = ifelse( is_significant==1, "*", "")  )

ggplot(stat_test_result_random_edges, aes(y= motif_type, x= parameter )) +
	geom_raster(aes(fill= -log10(boot_n_counts_adj_p_value+ 1/2000*15 ) )) +
	scale_fill_gradientn( colors=rev(heat.colors(5))) + # heat.colors
	theme( axis.text.y = element_text(face = "italic")) + 
	guides(fill=guide_colourbar(title=expression("-log"[10]*"(adjusted p-value)"))) + 
	geom_text( aes(label=is_significant_star   ))  + 
	xlab( "Proportion of negative genetic interactions added or removed") +
	ylab ('Triplet Motif Types')

ggsave(file.path(figures_results_directory, paste("randomization_collated_results_color_by_p_values", figure_file_suffix, sep="")), plot=last_plot() )

## Supplementary Figure 4. Analyze how filtering the negative genetic interaction by the stringency in fitness score affects the six types of triplet motifs. 
```{r}
